Effects of the body force on the evacuation dynamics

### 2019-12-20 paper.tex
mas correcciones de gramatica
correcciones de gramatica

\item[(ii)] Despite the reactive attitude $\tau$, the pedestrian addresses a 
``free'' (undisturbed) walking speed $\v_0$. This speed expresses his (her) 
motivation or intention to reach a certain destination (as comfortable as 
possible). Observations commonly associate $0.6\,$m/s, $1\,$m/s or $1.5\,$m/s 
to relaxed, normal or nervous walking speeds, respectively  
\cite{helbing_1995,helbing_2000,li_2015}.

@@

Network analysis is a set of techniques that characterize the structures in a graph. We defined the graph of contacts among individuals. In this graph, each node represents a pedestrian and the link between a pair of nodes is settled if this pair of pedestrians are in physical contact ($i.e.$ $r_{ij}<d_{ij}$).\\

@@

Increasing $v_d$ increases the mean degree in all cases. This happens because increasing $v_d$ produces higher densities that force individuals to touch each other. For a given $v_d$ the mean degree reduces as the $k$ value increases. In other words, the stiffer the pedestrians the less they touch each other. We will later discuss that this phenomenon is a characteristic of the bottleneck geometry that cannot be extrapolated to the corridor geometry.\\

Fig.~\ref{overlap_vd} shows the overlap as a function of $v_d$. The overlap is defined as $d_{ij}-r_{ij}$ where $d_{ij}$ is the sum of radius of particle $i$ and particle $j$ and $r_{ij}$  is the distance between both particles. In the range $v_d \geq 2$~m/s we can see that increasing $v_d$ increases the overlap (for all the $k$ values studied). For a given $v_d$, the overlap increases as the $k$ value decreases. Reducing $k$ means reducing the normal body force which allows a greater invasion of the personal space of the particles.\\

>>>>

\item[(ii)] Despite the reactive attitude $\tau$, the pedestrian addresses a 
``free'' (undisturbed) walking speed $v_0$. This speed expresses his (her) 
motivation or intention to reach a certain destination (as comfortable as 
possible). Observations commonly associate $0.6\,$m/s, $1\,$m/s or $1.5\,$m/s 
to relaxed, normal or nervous walking speeds, respectively  
\cite{helbing_1995,helbing_2000,li_2015}.

@@

Network analysis is a set of techniques that characterize the structures in a graph. We defined the graph of contacts among individuals. In this graph, each node represents a pedestrian and the link between a pair of nodes is settled if the pedestrians are in physical contact ($i.e.$ $r_{ij}<d_{ij}$).\\

@@

Increasing $v_d$ increases the mean degree in all the cases. This happens because increasing $v_d$ produces higher densities that force individuals to touch each other. For a given $v_d$ the mean degree reduces as the $k$ value increases. In other words, the stiffer the pedestrians the less they touch each other. We will later discuss that this phenomenon is restricted to the bottleneck geometry that cannot be extrapolated to the corridor geometry.\\

Fig.~\ref{overlap_vd} shows the overlap as a function of $v_d$. The overlap is defined as $d_{ij}-r_{ij}$ where $d_{ij}$ is the sum of radius of particle $i$ and particle $j$ and $r_{ij}$  is the distance between both particles. In the range $v_d \geq 2$~m/s we can see that increasing $v_d$ increases the overlap (for all the $k$ values studied). For a given $v_d$, the overlap increases as the $k$ value decreases. Reducing $k$ means reducing the normal body force which allows a greater invasion of the personal space of the individuals.\\
